---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/sosoc/roc.svg?branch=master)](https://travis-ci.org/sosoc/roc)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/sosoc/roc?branch=master&svg=true)](https://ci.appveyor.com/project/sosoc/roc)

# roc

The goal of roc is to allow R users to easily work with ocean colour data. 

## Installation

You can install roc from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("sosoc/roc")
```

## Example

This is a basic example to read a L3bin file and map it. 

```{r example}
## basic example code
```



There are helper functions to generate longitude / latitude coordinates for the bins (centre or corners). These bins
are a sparse, non-rectangular, grid on a Sinusoidal projection, see 

http://oceandata.sci.gsfc.nasa.gov/

http://oceancolor.gsfc.nasa.gov/SeaWiFS/TECH_REPORTS/PreLPDF/PreLVol32.pdf


Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.


# Note

An earlier version of this package imported from https://github.com/AustralianAntarcticDivision/rrshdf4 to read
the old HDF4 L3bin format.  This is no longer necessary, and read support is provided for the NetCDF 4.0 (HDF5)
version of the files from oceandata. 

